Improving credibility and efficiency of decision-making \\ within democratic communities via a statistical quorum

### 2018-04-19 statistical-quorum.tex
Layout not important for draft. No time to check as we are changing other stuff.
The vote to voting.

\section{Decision Credibility and Statistical Quorum}
\label{sec:decision-credibility}
A statistical quorum uses statistical hypothesis testing to infer the credibility of the outcome of an open vote before the community adopts the outcome as being truly representative all members' positions.
For example, in a community of 100 members, if 35 members support a specific proposal and 0 oppose, then we can conclude with high probability that, had all 100 members taken the time to vote, a majority of them would be in support of the proposal.  Hence, despite the reality of 65 members not having voted, the outcome of the 35-member vote was credible enough to be taken as representative of the entire community's desire.
On the other hand, if 80 members vote, where 41 support the proposal and 39 oppose, then we cannot yet conclude that the decision to accept the proposal is credible enough for the entire community to officially adopt, despite the significant participation in the vote.
Instead, the suggested course of action would be to continue gathering more votes and/or further discussing the proposal until a credible outcome is established.

@@

When considering a single proposal $X_i$ in isolation, we wish to compute:
\begin{align}\label{eq1}
\Pr(\alpha^*_i > T_i \mid X_i),
\end{align}
where
\begin{itemize}
\item[$\alpha^*_i = $] the total number of ``yes'' votes for $X_i$ if we were to sample the entire population,
\item[$T_i = $] $f \cdot N_i$, for some fraction $f$ corresponding to the type of majority needed for the vote
(e.g., $f=\frac{1}{2}$ for a simple majority).
\end{itemize}
Using the desirable prior
\begin{align}\label{eq2}
p_i \mid X_i \sim \operatorname{Beta}(1+\frac{\alpha_i}{K_i},1+\frac{\beta_i}{K_i}),
\end{align}
corresponding to a uniform prior when no votes have been cast ($\alpha_i = \beta_i = 0$), we can express \eqref{eq1} as:
\begin{align}\label{eq3}
\Pr(\alpha^*_i > T_i \mid X_i) &= 1 - {CDF}_{\nu_i}(V_i)
\end{align}
for
\begin{align*}
&\nu_i \sim \operatorname{Beta-Binomial}(1 + \frac{\alpha_i}{K_i}c, 1 + \frac{\beta_i}{K_i}c, K_i),\\
&{CDF}_{\nu_i}(V_i)  = \Pr(\nu_i \leq V_i),
\end{align*}
where
\begin{itemize}
\item[$V_i = $] $\lfloor{T_i - \alpha_i}\rfloor$, the maximum number of additional ``yes'' votes $X_i$ could receive such that it would remain below threshold.,
\item[$c = $] $10$, a hyperparameter chosen by the community based on their relative concern about false alarms versus (temporarily) missed detection.
\end{itemize}

>>>>

\section{Decision Credibility and Statistical Quorum}
\label{sec:decision-credibility}
A statistical quorum uses statistical hypothesis testing to infer the credibility of the outcome of an open vote before the community adopts the outcome as being truly representative all members' positions.
For example, in a community of 100 members, if 35 members support a specific proposal and 0 oppose, then we can conclude with high probability that, had all 100 members taken the time to vote, a majority of them would be in support of the proposal.  Hence, despite the reality of 65 members not having voted, the outcome of the 35-member vote was credible enough to be taken as representative of the entire community's desire.
On the other hand, if 80 members vote, where 41 support the proposal and 39 oppose, then we cannot yet conclude that the decision to accept the proposal is credible enough for the entire community to officially adopt, despite the significant participation in voting.
Instead, the suggested course of action would be to continue gathering more votes and/or further discussing the proposal until a credible outcome is established.

@@

When considering a single proposal $X_i$ in isolation, we wish to compute:
\begin{align}\label{eq1}
\Pr(\alpha^*_i > T_i \mid X_i),
\end{align}
where
\begin{itemize}
\item[$\alpha^*_i = $] the total number of ``yes'' votes for $X_i$ if we were to sample the entire population,
\item[$T_i = $] $f \cdot N_i$, for some fraction $f$ corresponding to the type of majority needed
(e.g., $f=\frac{1}{2}$ for a simple majority).
\end{itemize}
Using the desirable prior
\begin{align}\label{eq2}
p_i \mid X_i \sim \operatorname{Beta}(1+\frac{\alpha_i}{K_i},1+\frac{\beta_i}{K_i}),
\end{align}
corresponding to a uniform prior when no votes have been cast ($\alpha_i = \beta_i = 0$), we can express \eqref{eq1} as:
\begin{align}\label{eq3}
\Pr(\alpha^*_i > T_i \mid X_i) &= 1 - {CDF}_{\nu_i}(V_i)
\end{align}
for
\begin{align*}
&\nu_i \sim \operatorname{Beta-Binomial}(1 + \frac{\alpha_i}{K_i}c, 1 + \frac{\beta_i}{K_i}c, K_i),\\
&{CDF}_{\nu_i}(V_i)  = \Pr(\nu_i \leq V_i),
\end{align*}
where
\begin{itemize}
\item[$V_i = $] $\lfloor{T_i - \alpha_i}\rfloor$, the maximum number of additional ``yes'' votes $X_i$ could receive such that it would remain below threshold.,
\item[$c = $] $10$, a hyperparameter chosen by the community based on their relative concern about false alarms versus (temporarily) missed detection.
\end{itemize}
